*Platynereis dumerilii* three-day-old connectome --- cell-type compendium

### 2024-10-21 supplements/celltype_compendium_website/index.qmd
cell type compendium: clean up

[3D visualisation](_site/celltype_RGLs/celltype1.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype33.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype34.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype5.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype100.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype101.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype102.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype88.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype89.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype90.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype91.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype92.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype93.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype94.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype95.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype96.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype97.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype98.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype80.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype54.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype35.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype36.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype37.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype38.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype71.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype26.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype148.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype168.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype143.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype115.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype170.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype13.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype14.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype15.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype190.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype187.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype25.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype32.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype20.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype17.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype18.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype16.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype137.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype133.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype138.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype131.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype110.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype141.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype52.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype132.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype48.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype135.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype130.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype112.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype111.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype136.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype129.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype134.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype139.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype113.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype45.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype46.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype44.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype43.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype39.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype28.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype40.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype41.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype31.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype163.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype29.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype30.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype172.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype173.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype103.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype24.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype27.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype49.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype50.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype51.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype114.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype167.html){target="_blank"}

@@

![](snapshots/celltype2.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype2.html){target="_blank"}

@@

![](snapshots/celltype3.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype3.html){target="_blank"}

@@

![](snapshots/celltype171.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype171.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype11.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype12.html){target="_blank"}

@@

[3D visualisation](_site/celltype_RGLs/celltype10.html){target="_blank"}

@@

![](snapshots/celltype7.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype7.html){target="_blank"}

@@

![](snapshots/celltype6.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype6.html){target="_blank"}

@@

![](snapshots/celltype188.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype188.html){target="_blank"}

@@

![](snapshots/celltype193.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype193.html){target="_blank"}

@@

![](snapshots/celltype118.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype118.html){target="_blank"}

@@

![](snapshots/celltype174.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype174.html){target="_blank"}

@@

![](snapshots/celltype196.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype196.html){target="_blank"}

@@

![](snapshots/celltype57.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype57.html){target="_blank"}

@@

![](snapshots/celltype179.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype179.html){target="_blank"}

@@

![](snapshots/celltype55.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype55.html){target="_blank"}

@@

![](snapshots/celltype56.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype56.html){target="_blank"}

@@

![](snapshots/celltype123.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype123.html){target="_blank"}

@@

![](snapshots/celltype152.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype152.html){target="_blank"}

@@

![](snapshots/celltype153.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype153.html){target="_blank"}

@@

![](snapshots/celltype22.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype22.html){target="_blank"}

@@

![](snapshots/celltype124.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype124.html){target="_blank"}

@@

![](snapshots/celltype125.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype125.html){target="_blank"}

@@

![](snapshots/celltype117.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype117.html){target="_blank"}

@@

![](snapshots/celltype76.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype76.html){target="_blank"}

@@

![](snapshots/celltype175.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype175.html){target="_blank"}

@@

![](snapshots/celltype144.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype144.html){target="_blank"}

@@

![](snapshots/celltype199.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype199.html){target="_blank"}

@@

![](snapshots/celltype120.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype120.html){target="_blank"}

@@

![](snapshots/celltype121.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype121.html){target="_blank"}

@@

![](snapshots/celltype122.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype122.html){target="_blank"}

@@

![](snapshots/celltype197.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype197.html){target="_blank"}

@@

![](snapshots/celltype198.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype198.html){target="_blank"}

@@

![](snapshots/celltype189.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype189.html){target="_blank"}

@@

![](snapshots/celltype184.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype184.html){target="_blank"}

@@

![](snapshots/celltype140.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype140.html){target="_blank"}

@@

![](snapshots/celltype183.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype183.html){target="_blank"}

@@

![](snapshots/celltype185.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype185.html){target="_blank"}

@@

![](snapshots/celltype191.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype191.html){target="_blank"}

@@

![](snapshots/celltype192.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype192.html){target="_blank"}

@@

![](snapshots/celltype194.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype194.html){target="_blank"}

@@

![](snapshots/celltype195.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype195.html){target="_blank"}

@@

![](snapshots/celltype58.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype58.html){target="_blank"}

@@

![](snapshots/celltype4.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype4.html){target="_blank"}

@@

![](snapshots/celltype21.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype21.html){target="_blank"}

@@

![](snapshots/celltype23.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype23.html){target="_blank"}

@@

![](snapshots/celltype104.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype104.html){target="_blank"}

@@

![](snapshots/celltype116.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype116.html){target="_blank"}

@@

![](snapshots/celltype119.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype119.html){target="_blank"}

@@

![](snapshots/celltype126.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype126.html){target="_blank"}

@@

![](snapshots/celltype127.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype127.html){target="_blank"}

@@

![](snapshots/celltype160.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype160.html){target="_blank"}

@@

![](snapshots/celltype186.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype186.html){target="_blank"}

@@

![](snapshots/celltype201.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype201.html){target="_blank"}

@@

![](snapshots/celltype42.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype42.html){target="_blank"}

@@

![](snapshots/celltype53.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype53.html){target="_blank"}

@@

![](snapshots/celltype83.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype83.html){target="_blank"}

@@

![](snapshots/celltype202.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype202.html){target="_blank"}

@@

![](snapshots/celltype75.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype75.html){target="_blank"}

@@

![](snapshots/celltype60.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype60.html){target="_blank"}

@@

![](snapshots/celltype73.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype73.html){target="_blank"}

@@

![](snapshots/celltype74.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype74.html){target="_blank"}

@@

![](snapshots/celltype77.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype77.html){target="_blank"}

@@

![](snapshots/celltype78.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype78.html){target="_blank"}

@@

![](snapshots/celltype79.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype79.html){target="_blank"}

@@

![](snapshots/celltype149.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype149.html){target="_blank"}

@@

![](snapshots/celltype157.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype157.html){target="_blank"}

@@

![](snapshots/celltype147.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype147.html){target="_blank"}

@@

![](snapshots/celltype72.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype72.html){target="_blank"}

@@

![](snapshots/celltype145.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype145.html){target="_blank"}

@@

![](snapshots/celltype105.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype105.html){target="_blank"}

@@

![](snapshots/celltype70.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype70.html){target="_blank"}

@@

![](snapshots/celltype108.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype108.html){target="_blank"}

@@

![](snapshots/celltype109.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype109.html){target="_blank"}

@@

![](snapshots/celltype146.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype146.html){target="_blank"}

@@

![](snapshots/celltype150.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype150.html){target="_blank"}

@@

![](snapshots/celltype154.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype154.html){target="_blank"}

@@

![](snapshots/celltype155.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype155.html){target="_blank"}

@@

![](snapshots/celltype158.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype158.html){target="_blank"}

@@

![](snapshots/celltype169.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype169.html){target="_blank"}

@@

![](snapshots/celltype176.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype176.html){target="_blank"}

@@

![](snapshots/celltype177.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype177.html){target="_blank"}

@@

![](snapshots/celltype180.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype180.html){target="_blank"}

@@

![](snapshots/celltype200.png){height=200}
[3D visualisation](_site/celltype_RGLs/celltype200.html){target="_blank"}

>>>>

[3D visualisation](celltype_RGLs/celltype1.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype33.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype34.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype5.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype100.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype101.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype102.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype88.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype89.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype90.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype91.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype92.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype93.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype94.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype95.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype96.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype97.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype98.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype80.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype54.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype35.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype36.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype37.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype38.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype71.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype26.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype148.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype168.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype143.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype115.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype170.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype13.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype14.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype15.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype190.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype187.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype25.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype32.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype20.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype17.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype18.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype16.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype137.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype133.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype138.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype131.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype110.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype141.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype52.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype132.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype48.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype135.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype130.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype112.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype111.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype136.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype129.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype134.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype139.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype113.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype45.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype46.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype44.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype43.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype39.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype28.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype40.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype41.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype31.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype163.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype29.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype30.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype172.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype173.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype103.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype24.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype27.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype49.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype50.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype51.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype114.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype167.html){target="_blank"}

@@

![](snapshots/celltype2.png){height=200}
[3D visualisation](celltype_RGLs/celltype2.html){target="_blank"}

@@

![](snapshots/celltype3.png){height=200}
[3D visualisation](celltype_RGLs/celltype3.html){target="_blank"}

@@

![](snapshots/celltype171.png){height=200}
[3D visualisation](celltype_RGLs/celltype171.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype11.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype12.html){target="_blank"}

@@

[3D visualisation](celltype_RGLs/celltype10.html){target="_blank"}

@@

![](snapshots/celltype7.png){height=200}
[3D visualisation](celltype_RGLs/celltype7.html){target="_blank"}

@@

![](snapshots/celltype6.png){height=200}
[3D visualisation](celltype_RGLs/celltype6.html){target="_blank"}

@@

![](snapshots/celltype188.png){height=200}
[3D visualisation](celltype_RGLs/celltype188.html){target="_blank"}

@@

![](snapshots/celltype193.png){height=200}
[3D visualisation](celltype_RGLs/celltype193.html){target="_blank"}

@@

![](snapshots/celltype118.png){height=200}
[3D visualisation](celltype_RGLs/celltype118.html){target="_blank"}

@@

![](snapshots/celltype174.png){height=200}
[3D visualisation](celltype_RGLs/celltype174.html){target="_blank"}

@@

![](snapshots/celltype196.png){height=200}
[3D visualisation](celltype_RGLs/celltype196.html){target="_blank"}

@@

![](snapshots/celltype57.png){height=200}
[3D visualisation](celltype_RGLs/celltype57.html){target="_blank"}

@@

![](snapshots/celltype179.png){height=200}
[3D visualisation](celltype_RGLs/celltype179.html){target="_blank"}

@@

![](snapshots/celltype55.png){height=200}
[3D visualisation](celltype_RGLs/celltype55.html){target="_blank"}

@@

![](snapshots/celltype56.png){height=200}
[3D visualisation](celltype_RGLs/celltype56.html){target="_blank"}

@@

![](snapshots/celltype123.png){height=200}
[3D visualisation](celltype_RGLs/celltype123.html){target="_blank"}

@@

![](snapshots/celltype152.png){height=200}
[3D visualisation](celltype_RGLs/celltype152.html){target="_blank"}

@@

![](snapshots/celltype153.png){height=200}
[3D visualisation](celltype_RGLs/celltype153.html){target="_blank"}

@@

![](snapshots/celltype22.png){height=200}
[3D visualisation](celltype_RGLs/celltype22.html){target="_blank"}

@@

![](snapshots/celltype124.png){height=200}
[3D visualisation](celltype_RGLs/celltype124.html){target="_blank"}

@@

![](snapshots/celltype125.png){height=200}
[3D visualisation](celltype_RGLs/celltype125.html){target="_blank"}

@@

![](snapshots/celltype117.png){height=200}
[3D visualisation](celltype_RGLs/celltype117.html){target="_blank"}

@@

![](snapshots/celltype76.png){height=200}
[3D visualisation](celltype_RGLs/celltype76.html){target="_blank"}

@@

![](snapshots/celltype175.png){height=200}
[3D visualisation](celltype_RGLs/celltype175.html){target="_blank"}

@@

![](snapshots/celltype144.png){height=200}
[3D visualisation](celltype_RGLs/celltype144.html){target="_blank"}

@@

![](snapshots/celltype199.png){height=200}
[3D visualisation](celltype_RGLs/celltype199.html){target="_blank"}

@@

![](snapshots/celltype120.png){height=200}
[3D visualisation](celltype_RGLs/celltype120.html){target="_blank"}

@@

![](snapshots/celltype121.png){height=200}
[3D visualisation](celltype_RGLs/celltype121.html){target="_blank"}

@@

![](snapshots/celltype122.png){height=200}
[3D visualisation](celltype_RGLs/celltype122.html){target="_blank"}

@@

![](snapshots/celltype197.png){height=200}
[3D visualisation](celltype_RGLs/celltype197.html){target="_blank"}

@@

![](snapshots/celltype198.png){height=200}
[3D visualisation](celltype_RGLs/celltype198.html){target="_blank"}

@@

![](snapshots/celltype189.png){height=200}
[3D visualisation](celltype_RGLs/celltype189.html){target="_blank"}

@@

![](snapshots/celltype184.png){height=200}
[3D visualisation](celltype_RGLs/celltype184.html){target="_blank"}

@@

![](snapshots/celltype140.png){height=200}
[3D visualisation](celltype_RGLs/celltype140.html){target="_blank"}

@@

![](snapshots/celltype183.png){height=200}
[3D visualisation](celltype_RGLs/celltype183.html){target="_blank"}

@@

![](snapshots/celltype185.png){height=200}
[3D visualisation](celltype_RGLs/celltype185.html){target="_blank"}

@@

![](snapshots/celltype191.png){height=200}
[3D visualisation](celltype_RGLs/celltype191.html){target="_blank"}

@@

![](snapshots/celltype192.png){height=200}
[3D visualisation](celltype_RGLs/celltype192.html){target="_blank"}

@@

![](snapshots/celltype194.png){height=200}
[3D visualisation](celltype_RGLs/celltype194.html){target="_blank"}

@@

![](snapshots/celltype195.png){height=200}
[3D visualisation](celltype_RGLs/celltype195.html){target="_blank"}

@@

![](snapshots/celltype58.png){height=200}
[3D visualisation](celltype_RGLs/celltype58.html){target="_blank"}

@@

![](snapshots/celltype4.png){height=200}
[3D visualisation](celltype_RGLs/celltype4.html){target="_blank"}

@@

![](snapshots/celltype21.png){height=200}
[3D visualisation](celltype_RGLs/celltype21.html){target="_blank"}

@@

![](snapshots/celltype23.png){height=200}
[3D visualisation](celltype_RGLs/celltype23.html){target="_blank"}

@@

![](snapshots/celltype104.png){height=200}
[3D visualisation](celltype_RGLs/celltype104.html){target="_blank"}

@@

![](snapshots/celltype116.png){height=200}
[3D visualisation](celltype_RGLs/celltype116.html){target="_blank"}

@@

![](snapshots/celltype119.png){height=200}
[3D visualisation](celltype_RGLs/celltype119.html){target="_blank"}

@@

![](snapshots/celltype126.png){height=200}
[3D visualisation](celltype_RGLs/celltype126.html){target="_blank"}

@@

![](snapshots/celltype127.png){height=200}
[3D visualisation](celltype_RGLs/celltype127.html){target="_blank"}

@@

![](snapshots/celltype160.png){height=200}
[3D visualisation](celltype_RGLs/celltype160.html){target="_blank"}

@@

![](snapshots/celltype186.png){height=200}
[3D visualisation](celltype_RGLs/celltype186.html){target="_blank"}

@@

![](snapshots/celltype201.png){height=200}
[3D visualisation](celltype_RGLs/celltype201.html){target="_blank"}

@@

![](snapshots/celltype42.png){height=200}
[3D visualisation](celltype_RGLs/celltype42.html){target="_blank"}

@@

![](snapshots/celltype53.png){height=200}
[3D visualisation](celltype_RGLs/celltype53.html){target="_blank"}

@@

![](snapshots/celltype83.png){height=200}
[3D visualisation](celltype_RGLs/celltype83.html){target="_blank"}

@@

![](snapshots/celltype202.png){height=200}
[3D visualisation](celltype_RGLs/celltype202.html){target="_blank"}

@@

![](snapshots/celltype75.png){height=200}
[3D visualisation](celltype_RGLs/celltype75.html){target="_blank"}

@@

![](snapshots/celltype60.png){height=200}
[3D visualisation](celltype_RGLs/celltype60.html){target="_blank"}

@@

![](snapshots/celltype73.png){height=200}
[3D visualisation](celltype_RGLs/celltype73.html){target="_blank"}

@@

![](snapshots/celltype74.png){height=200}
[3D visualisation](celltype_RGLs/celltype74.html){target="_blank"}

@@

![](snapshots/celltype77.png){height=200}
[3D visualisation](celltype_RGLs/celltype77.html){target="_blank"}

@@

![](snapshots/celltype78.png){height=200}
[3D visualisation](celltype_RGLs/celltype78.html){target="_blank"}

@@

![](snapshots/celltype79.png){height=200}
[3D visualisation](celltype_RGLs/celltype79.html){target="_blank"}

@@

![](snapshots/celltype149.png){height=200}
[3D visualisation](celltype_RGLs/celltype149.html){target="_blank"}

@@

![](snapshots/celltype157.png){height=200}
[3D visualisation](celltype_RGLs/celltype157.html){target="_blank"}

@@

![](snapshots/celltype147.png){height=200}
[3D visualisation](celltype_RGLs/celltype147.html){target="_blank"}

@@

![](snapshots/celltype72.png){height=200}
[3D visualisation](celltype_RGLs/celltype72.html){target="_blank"}

@@

![](snapshots/celltype145.png){height=200}
[3D visualisation](celltype_RGLs/celltype145.html){target="_blank"}

@@

![](snapshots/celltype105.png){height=200}
[3D visualisation](celltype_RGLs/celltype105.html){target="_blank"}

@@

![](snapshots/celltype70.png){height=200}
[3D visualisation](celltype_RGLs/celltype70.html){target="_blank"}

@@

![](snapshots/celltype108.png){height=200}
[3D visualisation](celltype_RGLs/celltype108.html){target="_blank"}

@@

![](snapshots/celltype109.png){height=200}
[3D visualisation](celltype_RGLs/celltype109.html){target="_blank"}

@@

![](snapshots/celltype146.png){height=200}
[3D visualisation](celltype_RGLs/celltype146.html){target="_blank"}

@@

![](snapshots/celltype150.png){height=200}
[3D visualisation](celltype_RGLs/celltype150.html){target="_blank"}

@@

![](snapshots/celltype154.png){height=200}
[3D visualisation](celltype_RGLs/celltype154.html){target="_blank"}

@@

![](snapshots/celltype155.png){height=200}
[3D visualisation](celltype_RGLs/celltype155.html){target="_blank"}

@@

![](snapshots/celltype158.png){height=200}
[3D visualisation](celltype_RGLs/celltype158.html){target="_blank"}

@@

![](snapshots/celltype169.png){height=200}
[3D visualisation](celltype_RGLs/celltype169.html){target="_blank"}

@@

![](snapshots/celltype176.png){height=200}
[3D visualisation](celltype_RGLs/celltype176.html){target="_blank"}

@@

![](snapshots/celltype177.png){height=200}
[3D visualisation](celltype_RGLs/celltype177.html){target="_blank"}

@@

![](snapshots/celltype180.png){height=200}
[3D visualisation](celltype_RGLs/celltype180.html){target="_blank"}

@@

![](snapshots/celltype200.png){height=200}
[3D visualisation](celltype_RGLs/celltype200.html){target="_blank"}
